---
title: "portfolio-02"
author: "Ben Hardin"
date: "2023-02-07"
output: 
  html_document: 
    highlight: tango
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load tidyverse-plotly-dataset}
library(tidyverse)
library(plotly)

goals <- read.csv("data/TransposedGoals.csv")
```

### blah blah

```{r scatter, fig.height = 4, fig.width = 4}
ggplot(data = goals, aes(x = Avg_DisLikelihood, y = Avg_HonLikelihood))+
  geom_point()+
  theme_bw()+
  labs(title = "Scatterplot of Goal Expectancies",
       x = "Likelihood that dishonesty would achieve goal",
       y = "Likelihood that honesty would achieve goal")
ggsave("goals_scatter.png", plot = last_plot(), device = "png")

goals %>%
  summarize(r = cor(Avg_DisLikelihood, Avg_HonLikelihood))
```

### blah blah the 2nd
```{r dist stuff}
ggplot(goals, aes(x = Diff_Likelihood))+
  geom_histogram(fill = "grey", color = "black")+
  theme_bw()
```

```{r desc}
goals %>%
  summary
```

### blah blah the 3rd
```{r stuff}
polar_goals <- goals %>%
  filter(Diff_Likelihood >= 2.1 | Diff_Likelihood <= -1.4,
         Avg_HonLikelihood >= 3.0 | Avg_HonLikelihood <= 2.4,
         Avg_DisLikelihood >= 3.2 | Avg_DisLikelihood <= 2.00)

ggplot(data = polar_goals, aes(x = Avg_DisLikelihood, y = Avg_HonLikelihood))+
  geom_point(position = "jitter")+
  theme_bw()
```

```{r again}
polar_goals <- polar_goals %>%
  mutate(likelihood = if_else(Avg_HonLikelihood > 3.99, "Honesty", "Dishonesty"))
```

```{r groub}
polar_goals %>%
  group_by(likelihood) %>%
  count()
```

```{r tibble}
polar_goals %>%
  filter(likelihood == "Honesty") %>%
  arrange(desc(Diff_Likelihood)) %>%
  arrange(desc(Avg_HonLikelihood))

polar_goals %>%
  filter(likelihood == "Dishonesty") %>%
  arrange(Diff_Likelihood) %>%
    arrange(desc(Avg_DisLikelihood))
```

### Trying to make a fancy plot

So, first my goal is the make an interactive version of our scatterplot from earlier, that tells you the name of each goal when you hover over it. I also want to use color to more clearly emphasize the size of the difference between honesty and dishonesty scores for each goal.

1. [figuring out how to add layer]
2. [making an absolute value version of the diff score]

```{r interactive-scatter}
#absolute value differences
goals <- goals %>%
  mutate(abs_diff = abs(Diff_Likelihood))
  
goals_interactive <- goals %>%
  ggplot(aes(x = Avg_DisLikelihood, y = Avg_HonLikelihood, label = CASE_LBL))+
  geom_point(aes(color = abs_diff), position = "jitter")+
  theme_bw()

ggplotly(tooltip = c("label"))
```

[Should we make the goals have full names? Is that too much trouble?]

### Trying another one

What I would like to do now is select a few exemplar goals, which seem to (a) tap into most of the important themes/contents of goals and (b) represent a goals from the range of honesty vs. dishonesty

```{r selecting-exemplars}
goals %>%
  arrange(Diff_Likelihood)
```